The Impact of Educational Expenses of New Coders

### 2021-04-18 outputs/paper/paper.Rmd
Add RMSE

library(tidyverse)
library(dplyr)
library(janitor)
library(stargazer)
library(psych)
# install.packages("here")
library(here)
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
# install.packages("QuantPsyc")
library(QuantPsyc)
library(car)
library(kableExtra)
```

@@

## Formulae

@@

\begin{equation}
(\#eq:linRegModel1)
Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \epsilon
\end{equation}

@@

\begin{equation}
(\#eq:linRegModel2)
Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \epsilon
\end{equation}

@@

\begin{equation}
(\#eq:linRegModel3)
Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \beta_6X_6 + \epsilon
\end{equation}

@@

@@

```{r}
# TODO: RMSE
```

>>>>

library(tidyverse)
library(dplyr)
library(janitor)
library(stargazer)
library(psych)
# install.packages("here")
library(here)
# install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
# install.packages("QuantPsyc")
library(QuantPsyc)
library(car)
library(kableExtra)
# install.packages("forecast")
library(forecast)
```

@@

## Model formulae

@@

\begin{equation}
(\#eq:linRegModel1)
MoneyForLearning \sim \beta_0 + \beta_1 \times CityPopulation + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \epsilon
\end{equation}

@@

\begin{equation}
(\#eq:linRegModel2)
MoneyForLearning \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \epsilon
\end{equation}

@@

\begin{equation}
(\#eq:linRegModel3)
MoneyForLearning \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \beta_6X_6 + \epsilon
\end{equation}

@@

## Model validation
```{r}
#### Line plot for fitted values
plot(dfNewCoders$MoneyForLearning)
lines(multiReg1$fitted.values, col = "red")
lines(multiReg2$fitted.values, col = "blue")
lines(multiReg3$fitted.values, col = "green")

```{r}
#### RMSE ####
forecast::accuracy(multiReg1)
```

```{r}
#### RMSE with custom function ####
# Source: https://stackoverflow.com/questions/26237688/rmse-root-mean-square-deviation-calculation-in-r

RMSE <- function(error) {
  sqrt(mean(error^2)) 
}

RMSE(multiReg1$residuals)

@@
